Report

### 2020-06-25 Rmd/report.Rmd
Restore workflow and prepare poster for ICIS

# load data
stimuli.duration  <- fread(here("Data", "Stimuli", "stimuli_duration-aggregated.txt"))
data.sample       <- read_xlsx(here("Data", "Participant data", "data_participants.xlsx"))
data.fixations    <- fread(here("Data", "03_fixations.txt"))
trackloss         <- fread(here("Data", "02_filtered-trackloss.txt"))
results           <- fread(here("Data", "05_gca-results.txt"))
predictions       <- fread(here("Data", "05_gca-predictions.txt"))
multicollinearity <- fread(here("Data", "05_gca-multicollinearity.txt"))
```

@@

data.sample %>%
	filter(!Pilot, Valid, DateTest<now()) %>%
	select(ID, LangProfile, AgeGroup, Language, List, Sex) %>%
	group_by(LangProfile, AgeGroup, Language, List) %>%
	summarise(n = n()) %>%
	pivot_wider(id_cols = c("LangProfile", "AgeGroup", "Language"), names_from = "List", values_from = "n") %>%
	kable(digits = 0,
		  col.names = c("***LP***", "**Age group**", "**Language**", "**List 1**", "**List 2**", "**List 3**"), 
		  align = "c",
		  caption = "Sample size by age group, testing language, and list. Only participants that made it in the final sample are included.")

@@

trackloss %>%
	group_by(ParticipantID) %>%
	summarise(
		TracklossForParticipant = first(TracklossForParticipant),
		TracklossForParticipantSD = sd(TracklossForTrial, na.rm = TRUE)
		) %>%
	mutate(TracklossForParticipant = paste(printnum(TracklossForParticipant), "%"),
		   TracklossForParticipantSD = printnum(TracklossForParticipantSD)) %>%
	arrange(ParticipantID) %>%
	kable(digits = 3,
		  row.names = FALSE,
		  align = "c",
		  col.names = c("**Participant ID**", "**Mean**", "***SD***"),
		  caption = "Mean proportion of samples lost by trial.")

>>>>

# load data
stimuli.duration  <- fread(here("Data", "Stimuli", "stimuli_duration-aggregated.txt"))
data.sample       <- read_xlsx(here("Data", "Participant data", "data_participants.xlsx"))
data.fixations    <- fread(here("Data", "03_fixations.txt"))
attrition         <- fread(here("Data", "02_filtered-excluded-trials.txt"))
results           <- fread(here("Data", "05_gca-results.txt"))
predictions       <- fread(here("Data", "05_gca-predictions.txt"))
multicollinearity <- fread(here("Data", "05_gca-multicollinearity.txt"))
```

@@

data.sample %>%
	filter(!Pilot, Valid, DateTest<now()) %>%
	select(ID, LangProfile, AgeGroup, Language, List, Sex) %>%
	group_by(LangProfile, AgeGroup, Language, List) %>%
	summarise(n = n()) %>%
	pivot_wider(id_cols = c("LangProfile", "AgeGroup", "Language"), names_from = "List", values_from = "n") %>%
	mutate(Total = sum(`1`, `2`, `3`, na.rm = TRUE)) %>%

	kable(digits = 0,
		  col.names = c("***LP***", "**Age group**", "**Language**", "**List 1**", "**List 2**", "**List 3**", "**Total**"), 
		  align = "c",
		  caption = "Sample size by age group, testing language, and list. Only participants that made it in the final sample are included.")

@@

attrition %>%
	left_join(data.sample, by = c("ParticipantID" = "ID")) %>%
	summarise(
		TracklossForParticipant = first(TracklossForParticipant),
		TracklossForParticipantSD = sd(TracklossForTrial, na.rm = TRUE)
		) %>%
	mutate(TracklossForParticipant = paste(printnum(TracklossForParticipant), "%"),
		   TracklossForParticipantSD = printnum(TracklossForParticipantSD)) %>%
	arrange(ParticipantID) %>%
	kable(digits = 3,
		  row.names = FALSE,
		  align = "c",
		  col.names = c("**Participant ID**", "**Mean**", "***SD***"),
		  caption = "Mean proportion of samples lost by trial.")
